Seshadri constants of curve configurations on surfaces

### 2024-03-18 Response/Response to reviewer.tex

%\usepackage{tikz}https://www.overleaf.com/project/642e283246ec4730b8bdf398
\usepackage{csquotes}

\newcommand{\s}{\varepsilon}

\numberwithin{equation}{section}
\newtheorem{theorem}{Theorem}[section]
\newtheorem*{theorem*}{Theorem}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{definition}
\newtheorem{question}[theorem]{Question}

\begin{document}
\title{Response to Reviewer}
\begin{description}
\item [Mauscript Number] GMJ 231005 \\
\item [Title] Seshadri Constants of Curve Configurations on Surfaces
\item [Authors] Krishna Hanumanthu, Praveen Roy and Aditya Subramaniam
\end{description}

We thank the referee for carefully reading the manuscript and suggesting 
many useful changes and also for pointing out an error in the Assumption 2.1 which leads to 
ambiguities at several places. We fixed this error by assuming that the arrangement is connected.

We also agree with the referee that Example 2.21 can be shortened and it is better to 
focus on the computation of Seshadri constants.

Below we describe in detail the changes made to the manuscript based on the referee's comments. 
%We have made all these changes, and we hope that after making these changes, the paper has becomes more accessible for the readers and its overall quality has improved considerably.  Following are somewhat detailed explanation of changes that we have made on the basis of the report. \\
\begin{itemize}
\item Following the referee's suggestion, we included the assumption that the arrangement $\mathcal{C}$ is \textit{connected}. We added a remark immediately after Assumption 2.1 mentioning that the connectedness assumption implies that $C_i \cdot C_j > 0$ for all $i,j$.

\item We also removed the unnecessary assumption that all the curves do not meet at any point. Referee correctly noted that this is not necessary for the main results.

We only needed this assumption while computing the configurational Seshadri constants in Section 2.3. We therefore added the required assumption at the beginning of Seciton 2.3.

%agree with the referee about the problem in our way of using the Assumption 2.1. While writing the paper, we always had in mind the \textbf{connectedness of the arrangement}, 
%which we somehow missed to incorporate in the Assumption 2.1. We have now made it clear in the manuscript. \\
%\item Note that, now we don't require the semi-ampleness of divisor $A$ for $C_i^2$ to be positive, and it follows 
%from the connectedness of the arrangement. 
\item We retained the condition that all curves in our arrangements are linearly equivalent to a specific divisor. Many of the results and questions we state depend on this assumption. So removing this assumption will require a substantial re-working of the paper.

%Additionally, we would prefer to retain the second part of Assumption 2.1, as removing that requires 
%significant amount of additional work which we are currently not inclined to pursue. In-fact even the statement of Theorem 2.5 will change, if we remove the second assumption. 
%By the phrase `curves are linearly equivalent to a fixed divisor $A$', we mean that, $C_i \in |A|$ (linear system of $A$) for all $i$. \\

\item We have revised Example 2.21 considerably. We shortened it to focus solely on the computation of the Seshadri constant.
\end{itemize}

%We once again thank the referee for a quick review, we hope that we addressed all the concerns of the referee regarding this manuscript.

### 2024-03-18 sc-curve-config.tex
Changes made by Krishna-18 March (3:35 PM)

	\section{Seshadri constants for certain transversal curve arrangements}\label{main}	
	%\subsection{General results for any surface}
	We work with curve configurations on surfaces satisfying the following assumption. 
	\begin{assumption}\label{star1}
		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a \textcolor{red}{connected} transversal arrangement of curves
		on a complex smooth projective surface $X$ with the following properties: 
		\begin{itemize}
			\item There is no point where all the curves meet, i.e., $t_d=0.$
			\item  All the curves $C_i$ in $\mathcal{C}$ are linearly equivalent to a
			fixed divisor $A$ on $X$.
		\end{itemize}
	\end{assumption}

	\begin{definition}
		Let $\mathcal{C}$ be a transversal arrangement of curves on a smooth projective surface $X$
		satisfying Assumption \ref{star1}. Then we define the \emph{base constant} of $\mathcal{C}$ as 
		$${\rm bs}(\mathcal{C}) := {\rm max} \{t \, | \, t = \# \, C_{i} \cap {\rm Sing}(\mathcal{C}), \, C_{i} \in \mathcal{C}\},$$
		i.e., ${\rm bs}(\mathcal{C})$ is equal to the maximum number of singular points  of $\mathcal{C}$ that are contained in a single curve $C_{i} \in \mathcal{C}$.
	\end{definition}

@@

\subsection{Lower bounds on configurational Seshadri constants}\label{bounds}
We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.

@@

	\begin{theorem}\cite[Equation 4.9]{HS} \label{HTIn}
		Let $X$ be a ruled surface over a smooth curve of genus $g \geq 0$ with invariant $e
		\ge 4$.  Let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a transversal arrangement of curves
		satisfying Assumption \ref{star1} such that each curve in
		$\mathcal{C}$ is numerically equivalent to $A=aC_0+bf$ with $a > 0$
		and $b \ge ae$. Assume further that either $a\geq 2$ or if $a=1$, there exists a subset of four curves in $\mathcal{C}$ such that there is no point common to all the four curves. Then we have the following Hirzebruch-type inequality for $\mathcal{C}$:\\
		\begin{equation*}\label{eq:Hirzebruch type ineq}
			t_{2}+\frac{3}{4}t_{3} \geq -16+16g+\sum_{k\geq5}(2k-9)t_{k}+
			d(e(5a^2-2a)-10ab-4ag+4a+4b).\\
		\end{equation*}	
	\end{theorem}

@@

	We will now consider transversal configurations on surfaces of non-negative Kodaira dimension. We will use the following theorem. 
	\begin{theorem}\cite[Theorem 2.1]{LP1} \label{LP}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves having $d\geq 2$ irreducible components $C_1, \cdots, C_d.$ Then
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
	\end{theorem}
	We now give a lower bound on configurational Seshadri constants on surfaces of non-negative Kodaira dimension.
	\begin{theorem}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves satisfying Assumption \ref{star1}. Let $L$ be an ample line bundle on $X$. Then
		$$\varepsilon_{\mathcal{C}}(
		L) \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.$$
	\end{theorem}
	\begin{proof}
		As before, we find an upper-bound on the number $f_{1} = \sum_{r\geq 2} rt_{r}$. In order to do so, we are going to use Theorem \ref{LP} and Hirzebruch's inequality, namely
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
		Simplifying, we get 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+t_2+f_1-4f_0\leq 3c_2(X)-K_X^2.
		\end{equation*}	
		Since $t_2 \geq 0,$ we have 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+f_1-4f_0\leq 3c_2(X)-K_X^2
		\end{equation*}	
		and hence 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4f_0-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)).
		\end{equation*}	
		We know that
			$d \leq f_0 \leq C_1^2 {d \choose 2}$. So 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)). 
		\end{equation*}	
		Finally we obtain
		\begin{equation*}
			\varepsilon_\mathcal{C}(L)=\frac{d(L\cdot C_1)}{f_1} \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.
		\end{equation*}		
	\end{proof}

@@

\begin{example}
		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
		Then $X$ contains the following 48 lines (denoted by $l_{\alpha, \beta}$); 16 from each of the following three types: 
		\begin{eqnarray*}
			A: \quad x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta x_3, \\
			A': \quad x_0 = \alpha x_2 \; \text{and} \; x_1 = \beta x_3, \\
			A'': \quad x_0 = \alpha x_3 \; \text{and} \; x_1 = \beta x_2,
		\end{eqnarray*}
		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity. We fix two enumeration $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.

Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines. From the intersection behaviour of these lines, which is well known on Fermat quartic, it is clear that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}. It is also not difficult to see that the number of singular points on any line  in $\mathcal{L}$ is 10, as we show now. 
		It suffices to verify this assertion for a line of type $A$. Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$. We also know that each line of type $A$ meets 
		4 lines each of type $A'$ and $A''$ and these points are all double points. Therefore in all there are 10 singular points on a line of type $A$. By a similar argument one can show this for lines of type $A'$ and type $A''$ also.

		We now compute the multi-point Seshadri constant of $\mathcal{O}_X(1)$ at the singular locus of 
		the arrangement $\mathcal{L}$.  This arrangement has 216 singular points. So we have 
		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$
In fact, we claim that
		\[
		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
		\]
Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 
		\[
		\frac{\mathcal{O}_X(1)\cdot l_{\alpha_i,\beta_j}}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]
		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$
We now sum such inequalities over all the 48 lines and then we re-group the lines (as a set of 4), in such a way that sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore, we get
               \begin{eqnarray*}
                \sum\limits_{i=1}^{48} 2 C \cdot l_i &\ge& \sum\limits_{i=1}^{48} 2\left( \sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right) \\
                \Rightarrow  \sum\limits_{i=1}^{24} C \cdot \mathcal{O}_X(1) &\ge&  2\left( \sum\limits_{i=1}^{48}\sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).
               \end{eqnarray*}
Now, since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
		\begin{eqnarray*}
				24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{q_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{q_j}C \right) \\
		 &\geq& 4 \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}
		%%%%%
		\iffalse
		Using the sets  $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$  constructed above, we obtain
		\begin{eqnarray*}
		%2C\cdot \mathcal{L} = 
	\sum\limits_{i=1}^{48} C \cdot l_i &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow \sum\limits_{1}^{24} \mathcal{O}_X(1) \cdot C  &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow 24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{p_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{p_j}C \right) \\
		\Longrightarrow 24 \text{deg}(C) &\geq& 4 \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C \\
		\Longrightarrow 6 \text{deg}(C) &\geq&  \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}
		\fi
		%
		%%%
Here $\text{Sing}_2(\mathcal{L})$ and $\text{Sing}_4(\mathcal{L})$ denote the set of double points and the set of quadruple points of the arrangement $\mathcal{L}$, respectively. Therefore we get 
		\[
		\frac{\mathcal{O}_X(1) \cdot C}{\sum\limits_{p \in \text{Sing}(\mathcal{L})} \text{mult}_{p}C} = \frac{\text{deg}(C)}{ \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C} \geq \frac{1}{6} > \frac{1}{10}.
		\]
		This completes the proof of the claim.

@@

>>>>

	\section{Seshadri constants for certain transversal curve arrangements}\label{main}	
	%\subsection{General results for any surface}
	We work with curve configurations on surfaces satisfying the following assumption. 
	\begin{assumption}\label{star1}
		Let $\mathcal{C}=\{C_1,C_2, \ldots ,C_d\}$, $d\geq 4$ be a connected 
  transversal arrangement of curves 
		on a complex smooth projective surface $X$ such that all the curves 
  $C_i$ in $\mathcal{C}$ are linearly equivalent to a
			fixed divisor $A$ on $X$.
 % with the following properties: 
%		\begin{itemize}
%			\item There is no point where all the curves meet, i.e., $t_d=0.$
%			\item  All the curves $C_i$ in $\mathcal{C}$ are linearly equivalent to a
%			fixed divisor $A$ on $X$.
%		\end{itemize}
	\end{assumption}

 \begin{remark} 
Since each curve in $\mathcal{C}$ is assumed to be linearly equivalent to a fixed divisor $A$, the connectedness hypothesis in 
Assumption \ref{star1} implies in particular that $C_i\cdot C_j > 0$ for all $1\le i,j \le d$.  Note that the connectedness hypothesis will follow if $A^2 > 0$. 
 \end{remark}
	\begin{definition}
		Let $\mathcal{C}$ be a transversal arrangement of curves on a smooth projective surface $X$
		satisfying Assumption \ref{star1}. Then we define the \emph{base constant} of $\mathcal{C}$ as 
		$${\rm bs}(\mathcal{C}) := {\rm max} \{t \, | \, t = \# \, C_{i} \cap {\rm Sing}(\mathcal{C}), \, C_{i} \in \mathcal{C}\},$$
		i.e., ${\rm bs}(\mathcal{C})$ is equal to the maximum number of singular points  of $\mathcal{C}$ that are contained in a single curve $C_{i} \in \mathcal{C}$.
	\end{definition}

@@

\subsection{Lower bounds on configurational Seshadri constants}\label{bounds}
We now give some lower bounds on configurational Seshadri constants on ruled surfaces and on surfaces of non-negative Kodaira dimension.	We will 
work with arrangements of curves satisfying Assumption \ref{star1}. Further, we assume that 
there is no point where all the curves in $\mathcal{C}$ meet, i.e., $t_d=0.$

@@

	\begin{theorem}\cite[Equation 4.9]{HS} \label{HTIn}
		Let $X$ be a ruled surface over a smooth curve of genus $g \geq 0$ with invariant $e
		\ge 4$.  Let $\mathcal{C} = \{C_{1}, \ldots, C_{d}\}$ be a transversal arrangement of curves
		satisfying Assumption \ref{star1} such that each curve in
		$\mathcal{C}$ is numerically equivalent to $A=aC_0+bf$ with $a > 0$
		and $b \ge ae$. Assume further that all the curves in $\mathcal{C}$ do not meet in a point and that 
  either $a\geq 2$ or if $a=1$, there exists a subset of four curves in $\mathcal{C}$ such that there is no point common to all the four curves. Then we have the following Hirzebruch-type inequality for $\mathcal{C}$:\\
		\begin{equation*}\label{eq:Hirzebruch type ineq}
			t_{2}+\frac{3}{4}t_{3} \geq -16+16g+\sum_{k\geq5}(2k-9)t_{k}+
			d(e(5a^2-2a)-10ab-4ag+4a+4b).\\
		\end{equation*}	
	\end{theorem}

@@

	We will now consider transversal configurations on surfaces of non-negative Kodaira dimension. We will use the following theorem. 
	\begin{theorem}\cite[Theorem 2.1]{LP1} \label{LP}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves having $d\geq 2$ irreducible components $C_1, \cdots, C_d.$ Then
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
	\end{theorem}
	We now give a lower bound on configurational Seshadri constants on surfaces of non-negative Kodaira dimension.
	\begin{theorem}
		Let $X$ be a smooth complex projective surface with non-negative Kodaira dimension and let $C=C_1 + \cdots + C_d$ be a transversal configuration of smooth curves satisfying Assumption \ref{star1}. Assume further that all the curves in $\mathcal{C}$ do not meet in a point. 
  Let $L$ be an ample line bundle on $X$. Then
		$$\varepsilon_{\mathcal{C}}(
		L) \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.$$
	\end{theorem}
	\begin{proof}
		As before, we find an upper-bound on the number $f_{1} = \sum_{r\geq 2} rt_{r}$. In order to do so, we are going to use Theorem \ref{LP} and Hirzebruch's inequality, namely
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))-t_2+\sum_{r \geq 3} (r-4)t_r \leq 3c_2(X)-K_X^2.
		\end{equation*}
		Simplifying, we get 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+t_2+f_1-4f_0\leq 3c_2(X)-K_X^2.
		\end{equation*}	
		Since $t_2 \geq 0,$ we have 
		\begin{equation*}
			K_X \cdot C + 4 \sum_{i=1}^{d} (1-g(C_i))+f_1-4f_0\leq 3c_2(X)-K_X^2
		\end{equation*}	
		and hence 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4f_0-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)).
		\end{equation*}	
		We know that
			$d \leq f_0 \leq C_1^2 {d \choose 2}$. So 
		\begin{equation*}
			f_1\leq 3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i)). 
		\end{equation*}	
		Finally we obtain
		\begin{equation*}
			\varepsilon_\mathcal{C}(L)=\frac{d(L\cdot C_1)}{f_1} \geq \frac{d(L\cdot C_1)}{3c_2(X)-K_X^2+4C_1^2 {d \choose 2}-K_X \cdot C-4 \sum_{i=1}^{d} (1-g(C_i))}.
		\end{equation*}		
	\end{proof}

@@

\begin{example}
		Let $X \subset \mathbb{P}^3$ be a Fermat quartic defined by the vanishing locus of $x_0^4 + x_1^4 + x_2^4 + x_3^4$, where $x_0, \ldots, x_3$ are the coordinates of $\mathbb{P}^3$. 
		Then $X$ contains the following 48 lines; 
  %(denoted by $l_{\alpha, \beta}$); 
  16 from each of the following three types: 
		\begin{eqnarray*}
			A: \quad x_0 = \alpha x_1 \; \text{and} \; x_2 = \beta x_3, \\
			A': \quad x_0 = \alpha x_2 \; \text{and} \; x_1 = \beta x_3, \\
			A'': \quad x_0 = \alpha x_3 \; \text{and} \; x_1 = \beta x_2,
		\end{eqnarray*}
		where $\alpha, \beta \in \{\zeta, -\zeta, i\zeta, -i\zeta \}$ and $\zeta$ is a primitive eighth root of unity. We fix two enumerations $\alpha_i, \beta_j$, for $1\leq i, j \leq 4$ of the set $\{\zeta, -\zeta, i\zeta, -i\zeta \}$.

Now let $\mathcal{L} = \{l_1,l_2, \ldots,  l_{48}\}$ be the arrangement consisting of all these 48 lines. 
Intersection behaviour of lines on a Fermat quartic is classically well-known. 
%From the intersection behaviour of these lines, which is well known on Fermat quartic, 
In particular, it is known that the only singular points for the arrangement $\mathcal{L}$ are either double points or quadruple points; \cite[Example 3.3]{Pok1}. It is also not difficult to see that the number of singular points on any line $l$ in $\mathcal{L}$ is 10. Of these, two are quadruple points obtained by intersecting $l$ with lines of the same type. The remaining eight points are double points obtained by intersecting $l$ with lines of different types.

{\color{red} Can we remove the following paragraph?}

For the convenience of the reader, we quickly recall the argument below.  
		It suffices to verify this assertion for a line of type $A$. Given a line, denoted by $l_{\alpha_i,\beta_j}$ of type $A$, we know that it has two quadruple points $[\alpha_i :1 :0 :0]$ and $[0 :0 :\beta_j :1]$. 
		In fact, these points are obtained by intersecting the lines in $\{l_{\alpha_i,\beta_j} \mid 1\leq j \leq 4 \} = X \cap V(x_0 - \alpha_i x_1)$ with those in  $\{l_{\alpha_i,\beta_j} \mid 1\leq i \leq 4 \} = X \cap V(x_2 - \beta_j x_3)$. 
		Note also that the sum of lines from any one of these sets is linearly equivalent to $\mathcal{O}_X(1)$. We also know that each line of type $A$ meets 
		4 lines each of type $A'$ and $A''$ and these points are all double points. Therefore in all there are 10 singular points on a line of type $A$. By a similar argument one can show this for lines of type $A'$ and type $A''$.

		We now compute the multi-point Seshadri constant of $\mathcal{O}_X(1)$ at the singular locus of 
		the arrangement $\mathcal{L}$.  This arrangement has 216 singular points. So we have 
		$$\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) \le \sqrt{\frac{4}{216}} \sim 0.136.$$
In fact, we claim that
		\[
		\varepsilon(X, \mathcal{O}_X(1), \text{Sing}(\mathcal{L})) = \frac{1}{10}.
		\]
Note that each line $l_{\alpha_i,\beta_j}$ has degree 1 in $\mathbb{P}^3$. So,  from the above discussion, it is clear that 
		\[
		\frac{\mathcal{O}_X(1)\cdot l_{\alpha_i,\beta_j}}{10} %= \frac{(l_{\alpha_i,\beta_1} + l_{\alpha_i,\beta_2} + l_{\alpha_i,\beta_3} + l_{\alpha_i,\beta_4})\cdot  l_{\alpha_i,\beta_j} }{10} 
		= \frac{1}{10}.
		\]
		Now let $C \subset X$ be any reduced and irreducible curve such that $C \notin \mathcal{L}$ and which passes through some point in the singular locus of 
		$\mathcal{L}$. By B\'ezout's theorem, we have the following inequality for every line $l \in \mathcal{L}$:
		$$2 C \cdot l \ge 2\left( \sum_{p \in l \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).$$

We now sum such inequalities over all the 48 lines and then group the lines into sets of four lines, in such a way that the sum of each group corresponds to $\mathcal{O}_X(1)$.  Therefore we get
               \begin{eqnarray*}
                \sum\limits_{i=1}^{48} 2 C \cdot l_i &\ge& \sum\limits_{i=1}^{48} 2\left( \sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right) \\
                \Rightarrow  \sum\limits_{i=1}^{24} C \cdot \mathcal{O}_X(1) &\ge&  2\left( \sum\limits_{i=1}^{48}\sum_{p \in l_i \,\cap \,\text{Sing} (\mathcal{L})} \text{mult}_p C \right).
               \end{eqnarray*}

Since each double point appears in two lines and each quadruple point appears in four lines, we obtain 
		\begin{eqnarray*}
				24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{q_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{q_j}C \right) \\
		 &\geq& 4 \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}
		%%%%%
		\iffalse
		Using the sets  $\mathcal{L}_1$, $\mathcal{L}_2$, \ldots, $\mathcal{L}_{24}$  constructed above, we obtain
		\begin{eqnarray*}
		%2C\cdot \mathcal{L} = 
	\sum\limits_{i=1}^{48} C \cdot l_i &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow \sum\limits_{1}^{24} \mathcal{O}_X(1) \cdot C  &\geq& 2\sum\limits_{p\in \text{Sing}(\mathcal{L})} \text{mult}_pC \\ 
		\Longrightarrow 24 \text{deg}(C) &\geq& 2 \left(2\sum\limits_{p_i \in \text{Sing}_2(\mathcal{L})} \text{mult}_{p_i} C ~+~ 4\sum\limits_{p_j \in \text{Sing}_4(\mathcal{L})} \text{mult}_{p_j}C \right) \\
		\Longrightarrow 24 \text{deg}(C) &\geq& 4 \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C \\
		\Longrightarrow 6 \text{deg}(C) &\geq&  \sum\limits_{p \in C\cap \text{Sing}(\mathcal{L})} \text{mult}_{p}C.
		\end{eqnarray*}
		\fi
		%
		%%%

Here $\text{Sing}_2(\mathcal{L})$ and $\text{Sing}_4(\mathcal{L})$ denote the set of double points and the set of quadruple points of the arrangement $\mathcal{L}$, respectively. Therefore we get 
		\[
		\frac{\mathcal{O}_X(1) \cdot C}{\sum\limits_{p \in \text{Sing}(\mathcal{L})} \text{mult}_{p}C} = \frac{\text{deg}(C)}{ \sum\limits_{p \in\text{Sing}(\mathcal{L})} \text{mult}_{p}C} \geq \frac{1}{6} > \frac{1}{10}.
		\]
		This completes the proof of the claim.

@@

 \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper and for giving many corrections and useful comments which substantially improved the paper. The first author is partially supported by a grant from Infosys Foundation.
